---
title: "EDA LA-1 REPORT"
author: "AMOGH JAVALI USN : 1NT21IS026"
date: "2024-01-26"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HOTEL BOOKINGS DEMAND DATASET

## Load a dataset:
```{r}
my_data <- read.csv("C:/Users/amogh/Desktop/Dataset/amogh.csv")
```

## Packages:
```{r}
install.packages("base")
library(base)
```

## Help and Documentation:
```{r}
?mean
```

## View the first few rows of the dataset:
```{r}
head(my_data)
```

## View the structure of the dataset:
```{r}
str(my_data)
```


## Summary statistics:
```{r}
summary(my_data)
```


## Basic plot:
```{r}
plot(my_data$Adults, my_data$Children)
```


## Histogram:
```{r}
hist(my_data$Adults)
```

## Boxplot:
```{r}
boxplot(my_data$Adults)
```

## Calculate mean:
```{r}
mean(my_data$Adults)
```

## Calculate median:
```{r}
median(my_data$Adults)

```

## Data Manipulation:
## Filter rows based on a condition:
```{r}
subset_data <- my_data[my_data$Adults > 100, ]
head(subset_data, n = 10)
```

## Create a new variable:
```{r}
my_data$new_variable <- my_data$Adults + my_data$Children
head(my_data$new_variable, n = 10)
```

## Rename a variable:
```{r}
names(my_data)[2] <- "Hotel"
```

## Remove a variable:
```{r}
my_data$Babies <- NULL
head(my_data, n = 10)
```


## Sort data by a variable:
```{r}
my_data <- my_data[order(my_data$Adults), ]
```

## Data Exploration:
## Correlation matrix:
```{r}
cor(my_data$Adults, my_data$Children)
```

## Frequency table:
```{r}
table_freq <- table(my_data$Adults)
head(table_freq, n = 50)
```

## Descriptive statistics by group:
```{r}
table_tap <- tapply(my_data$Adults, my_data$Children, summary)
head(table_tap, n = 10)
```

## Missing Data Handling:
## Check for missing values:
```{r}
any(is.na(my_data))
```

## Remove missing values:
```{r}
my_data_no_na <- na.omit(my_data)
```

## Impute missing values:
```{r}
my_data$High[is.na(my_data$Adults)] <- mean(my_data$Adults, na.rm = TRUE)
```

## Statistical Analysis:
## t-test:
```{r}
result <- t.test(my_data$Adults)
result
```

## ANOVA:
```{r}
anova_model <- aov(Adults ~ Children, data = my_data)
summary(anova_model)
```

## Linear Regression:
```{r}
lm_model <- lm(Adults ~ Children, data = my_data)
summary(lm_model)
```

## Chi-square test:
```{r}
chisq.test(table(my_data$Adults, my_data$Children))
```

## Advanced Visualization:
## ggplot2 - Scatter plot:
```{r}
library(ggplot2)
ggplot(my_data, aes(x = Adults, y = Children)) +
  geom_point()
```

## ggplot2 - Boxplot:
```{r}
ggplot(my_data, aes(x = Adults, y = Children)) +
  geom_boxplot()
```

## ggplot2 - Histogram:
```{r}
ggplot(my_data, aes(x = Adults)) +
  geom_histogram()
```

## Time Series Analysis:
## Convert to time series:
```{r}
my_time_series <- ts(my_data$Adults, start = 1, end = length(my_data$Children), frequency = 1)
head(my_time_series, n = 10) 
```

## Time series plot:
```{r}
plot(my_time_series)
```

## ARIMA modeling:
```{r}
arima_model <- arima(my_time_series, order = c(1,1,1))
arima_model
```